MS5130 A3 Clothing_Product_Analysis

### 2024-04-01 MS5130_A3_Clothing_Product_Analysis.qmd
Insights 3.0
Added leaflet to showcase top3 brands for each country

library(ggplot2) # For visualization
library(dplyr) # For data manipulation
library(tidyr) # For tidying data
library(stringr) # For string manipulation
library(readr) # For reading CSV files
library(tidytext)
library(plotly)
library(wordcloud)
library(quanteda)
```

@@

# Reading the CSV File
product_catalog <- read_csv("C:/Users/manav/OneDrive/Desktop/Work/R_Applied_Analytics/Assignment 3/myntra_products_catalog.csv")

@@

Product_Detailed_2 <- read_csv("C:/Users/manav/OneDrive/Desktop/Work/R_Applied_Analytics/Assignment 3/Product_Detailed_2.csv")
Product_Reviews_3 <- read_csv("C:/Users/manav/OneDrive/Desktop/Work/R_Applied_Analytics/Assignment 3/Product_Reviews_3.csv")

@@

@@

# Preprocessing to remove punctuations, numbers, spaces and common english words like 'the', 'at' since they are not relevant for analysis
cleaned_corpus <- text_corpus %>%
  tokens() %>%
  tokens_tolower() %>%
  tokens_remove(pattern = "[[:punct:]]") %>%
  tokens_remove(pattern = "\\d+") %>%
  tokens_remove(pattern = stopwords("en")) %>%
  tokens_remove(pattern = "[[:space:]]+")

@@

# We will first create two separate data frames for each year
df_2015 <- top_brands_combined %>% filter(Year == "2015")
df_2020 <- top_brands_combined %>% filter(Year == "2020")

@@

# Combining the two plots into one with two subplots
# Note: shareX = TRUE means that all subplots will share the same x-axis.
subplot(p1, p2, nrows = 2, shareX = TRUE) %>%
  layout(title = 'Average Prices by Brand for 2015 and 2020')

@@

>>>>

library(ggplot2) # For visualization
library(dplyr) # For data manipulation
library(tidyr) # For tidying data
library(stringr) # For string manipulation
library(readr) # For reading CSV files
library(tidytext) 
library(plotly)
library(wordcloud)
library(quanteda)
library(leaflet)
library(tidygeocoder)

@@

# Reading the CSV File
product_catalog <- read_csv("myntra_products_catalog.csv")

@@

Product_Detailed_2 <- read_csv("Product_Detailed_2.csv")
Product_Reviews_3 <- read_csv("Product_Reviews_3.csv")

@@

The histogram shows a normal distribution for the sentiment scores, most scores cluster around the middle, suggesting that most sentiments expressed are neutral. There are fewer very positive or very negative sentiments, as seen by the lower bars at the ends.

This bar chart displays average sentiment scores for different clothing categories. Tops, Dresses, and Jackets seem to have higher average sentiments, indicating more positive feedback, while the 'Trend' category has a noticeably lower average sentiment score.

@@

# Preprocessing to remove punctuations, numbers, spaces and common english words like 'the', 'at' since they are not relevant for analysis
cleaned_corpus <- text_corpus %>%
  tokens() %>%
  tokens_tolower() %>%
  tokens_remove(pattern = "[[:punct:]]") %>%
  tokens_remove(pattern = "\\d+") %>%
  tokens_remove(pattern = stopwords("en")) %>%
  tokens_remove(pattern = "[[:space:]]+")
# Adapted from: https://search.r-project.org/CRAN/refmans/quanteda/html/tokens_select.html

@@

df_2015 <- top_brands_combined %>% filter(Year == "2015")
df_2020 <- top_brands_combined %>% filter(Year == "2020")

@@

# Combining the two plots into one with two subplots
# Note: shareX = TRUE means that all subplots will share the same x-axis.
subplot(p1, p2, nrows = 2, shareX = TRUE) %>%
  layout(title = 'Average Prices by Brand for 2015 and 2020')
# Adapted from: https://plotly.com/r/subplots/

@@

## Brand location on world map using leaflet

# Loading the dataset that contains brands along with their founding country
location_of_brands <- read.csv("Location_of_brands.csv")

head(location_of_brands)

# Finding lat and long using OSM geocoding
geocoded_data <- location_of_brands %>%
  geocode(country = location, method = 'osm') %>%
 # Adapted from: https://geocoder.readthedocs.io/providers/OpenStreetMap.html
  distinct(location, .keep_all = TRUE) %>%
  select(location,lat,long)

print(geocoded_data)

# Joining the lat and long with the brands with location dataset
brand_location_geocoded <- inner_join(location_of_brands, geocoded_data, by = "location", relationship = "many-to-many") %>%
  select (Brands,location,lat,long)

head(brand_location_geocoded)

# Aggregating the data from detailed dataset 2 at brand level
aggregated_brands <- Product_Detailed_2 %>%
  group_by(BrandName) %>%
  summarise(
    AvgPrice = mean(`OriginalPrice (in Rs)`, na.rm = TRUE),
    ProductCount = n()
  ) %>%
  ungroup() %>%
  select(Brands = BrandName, AvgPrice, ProductCount)

# Using the Brand aggregated dataset and brand geocoded dataset to create a list of top 3 brands for each country and product count for those brands

top_brands_by_country <- aggregated_brands %>%
  inner_join(brand_location_geocoded, by = "Brands") %>%
  group_by(location) %>%
  arrange(desc(AvgPrice)) %>%
  mutate(Rank = row_number()) %>%
  filter(Rank <= 3) %>%
  summarise(
    TopBrands = paste(Brands, "(", round(AvgPrice, 2), "INR - ", ProductCount, "products)", collapse = "<br>")
  ) %>%
  ungroup()

# Joining back with 'geocoded_data' to get latitude and longitude
country_info <- geocoded_data %>%
  distinct(location, .keep_all = TRUE) %>%
  inner_join(top_brands_by_country, by = "location")

print(country_info)

# Creating the world map using leaflet
leaflet(country_info) %>%
  addProviderTiles(providers$CartoDB.Voyager) %>%
  # Adapted from: https://www.kaggle.com/code/devzohaib/interactive-maps-with-leaflet-in-r
  addCircleMarkers(
    lng = ~long, lat = ~lat, radius = 8, color = "coral", fillOpacity = 0.8,
    popup = ~paste0("<strong>", location, "</strong><br><strong>Top 3 Brands:</strong><br>", TopBrands)
  ) %>%
  setView(lng = 20, lat = 0, zoom = 2)
